Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-09-09 sections/introduction.tex
updated

\begin{figure}
  \sidecaption
  \includegraphics{gr/intro/Fig_SICM-and-Light-resolution}%
  \caption{\textbf{Hypothetical fluorescence analysis of proteins in the boar
      spermatozoon.} \textbf{A:} Proteins A and B in the stable structures
    observed by SICM. \textbf{B:} Hypothetical positions of the fluorescent
    labels of proteins A and B. Scale bar: 200\,nm \textbf{C:} Computed
    fluorescence image.}
  \label{fig:sicm-and-light-resolution}
\end{figure}
In all stable structures in the recordings (highlighted by
the dashed lines) at least one group of three protrusions arranged in a line
are observable. If one assumes, without any biological support and just to be
able to exemplify the impact of the limited resolution of light microscopy,
that such a row is comprised of two different proteins, one at the first and
last position (magenta arrows in Fig.~\ref{fig:sicm-and-light-resolution}A),
and the other one on the central spot (green arrows in Fig.~\ref{fig:sicm-and-light-resolution}A), and one further assumes
that the two different proteins have been labelled by two different markers
(the positions of the markers are indicated by the magenta and green dots in Fig.~\ref{fig:sicm-and-light-resolution}B),
the resulting light microscopy images would result in

>>>>

\begin{figure}
  \sidecaption
  \includegraphics{gr/intro/Fig_SICM-and-Light-resolution}%
  \caption{\textbf{Hypothetical fluorescence analysis of proteins in the boar
      spermatozoon.} \textbf{A:} Proteins A and B in the stable structures
    observed by SICM. \textbf{B:} Hypothetical positions of the fluorescent
    labels of proteins A and B. Scale bar: 200\,nm \textbf{C:} Computed
    fluorescence image, resolutions were 250\,nm for the magenta and 300\,nm
    for the green marker.}
  \label{fig:sicm-and-light-resolution}
\end{figure}
In all stable structures in the recordings (highlighted by the dashed lines)
at least one group of three protrusions arranged in a line are observable. To
exemplify the impact of the limited resolution of light microscopy, assume,
without any biological support, that such a complex is comprised of two
different proteins A and B, which float in the plasma membrane until they form
the complex. In the complex, protein A is located at the first and last
position (magenta arrows in Fig.~\ref{fig:sicm-and-light-resolution}A), and
protein B on the central spot (green arrows in
Fig.~\ref{fig:sicm-and-light-resolution}A). Further, assume that the two
different proteins have been labelled by two different fluorescent markers
(the positions of the markers are indicated by the magenta and green dots in
Fig.~\ref{fig:sicm-and-light-resolution}B) and a correlating light microscopic
image has been recorded (Fig.~\ref{fig:sicm-and-light-resolution}C) to analyze
the molecular composition of the stable structures.

Due to the limited resolution, the fluorescence image consists of overlapping
spots of the two different markers and looks blurred, compared to the
SICM topography image. Although co-localisation of the two proteins can be
observed at the positions of the stable structures, it is hard if not
impossible to allocate the fluorescent spots to protrusions in the topography
image.
